\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=0.8in}
\usepackage{color}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5} % For icons

% Define colors
\definecolor{headerblue}{RGB}{41, 128, 185}
\definecolor{sectiongray}{RGB}{96, 96, 96}

% Formatting the title
\titleformat{\section}{\color{headerblue}\scshape\Large}{}{0em}{}
\titleformat{\subsection}{\color{sectiongray}\bfseries}{}{0em}{}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Samir Rizk}} \\
    \vspace{2mm}
    \textcolor{headerblue}{\textit{Embedded Linux Engineer}} \\
\end{center}

% Contact Details with Icons
\begin{center}
    \faMapMarker \ Giza, Egypt \quad
    \faLinkedin \ \href{https://www.linkedin.com/in/samir-rizk-3174b4207/}{LinkedIn} \quad
    \faGithub \ \href{https://github.com/SamRizk}{GitHub} \quad
    \faCode \ \href{https://codeforces.com/profile/SaMir_R_}{Codeforces} \quad
    \faHackerrank \ \href{https://www.hackerrank.com/profile/samir9999live}{HackerRank} \quad
    \faCode \ \href{https://www.codechef.com/users/samir_9999}{CodeChef} \quad
    \faEnvelope \ Gmail
\end{center}

\noindent\rule{\linewidth}{0.5mm} % Horizontal line

\vspace{-3mm}
\section*{Profile}
Computer Engineer passionate about solving complex problems with innovative programming approaches. Currently working as an Embedded Software Engineer with experience in designing, developing, and maintaining embedded software systems. Highly motivated with strong leadership skills, a keen interest in security, real-time systems, and networking in Linux.

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Education}
\noindent
\textbf{Embedded Systems 9-Month Program} \\
\textit{Information Technology Institute (ITI)}, Smart Village, Egypt \hfill \textbf{Oct 2022 – Jun 2023} \\
\textcolor{sectiongray}{Graduation Project: RTOS implementation from scratch}

\vspace{1mm}
\noindent
\textbf{B.Sc. in Computer Engineering} \\
\textit{Faculty of Engineering, Al-Azhar University}, Nasr City, Egypt \hfill \textbf{Sep 2017 – Jul 2022} \\
\textcolor{sectiongray}{Graduation Project: Autonomous Delivery System}

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Experience}
\noindent
\textbf{Embedded Software Engineer} \\
\textit{Valeo, Egypt} \hfill \textbf{2023 – Present} \\
\begin{itemize}[leftmargin=*]
    \item Developed security features for the Artemis project for Mercedes, with the target ECU developed by Qualcomm. Focus areas included DAC, core dump analysis, SSH, SCP, and Linux security configurations.
    \item Feature owner for the Flashing feature in the ConMod project for Volkswagen, where the target ECU was developed by Quectel. Implemented efficient one-click flashing using QFIL in console mode, enhancing flashing speed and reliability.
    \item Worked extensively with CANoe, DLT Viewer, GDB, and other embedded development and debugging tools.
    \item Gained expertise in system-level development using ADB, vsomeip, Franca, systemd, systemv, udev, sudoers, groups, iptables, and Yocto.
    \item Developed automated test cases using Python for validation and verification of embedded systems.
\end{itemize}

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Skills}
\noindent
\textbf{Programming Languages:} C, C++, Python, Java, Bash, Batch Scripting \\
\textbf{Tools:} Git, Make, CMake, GDB, CANoe, DLT Viewer, Yocto, Systemd, Systemv, ADB \\
\textbf{Embedded Systems:} Embedded Linux, RTOS, Microcontrollers (ATMEGA32, STM32), Communication Protocols (UART, SPI, I2C, CAN, LIN) \\
\textbf{Security Features:} Linux Security (udev, sudoers, groups, DAC, iptables), SSH, SCP \\
\textbf{Software Development:} Data Structures \& Algorithms, Debugging, Automation Testing with Python

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Programming Contests Activity}
\begin{itemize}[leftmargin=*]
    \item Solved +1200 algorithmic challenges on different online judges.
    \item Participated in \href{https://drive.google.com/file/d/1L2w-xp9LEYIkzK9PAs0-Fbm2yFh7iffF/view}{Al-Azhar Collegiate Programming Contest (2020)}.
\end{itemize}

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Soft Skills}
\begin{itemize}[leftmargin=*]
    \item Communication and Leadership
    \item Time Management and Teamwork
    \item Presentation and Problem-Solving Skills
\end{itemize}

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{Languages}
\noindent
\textbf{Arabic:} Native \\
\textbf{English:} B2 - C1 Proficiency

\noindent\rule{\linewidth}{0.3mm} % Section break line

\section*{References}
Available upon request.

\end{document}
